Dependent Object Types

### 2012-07-01 doc/semester/report.tex
typo

\section{Conclusion and Future Work}\label{conclusion}
This semester's work was instructive in pointing out the problematic
aspects of the original DOT calculus, and exploring some possible
fixes. However, I haven't been able to reach a revised calculus
without soundness hole. Furthermore, I believe that the revised
calculus with all the patches is not as elegant as the original
calculus. Going forward, I want to take a broader view by by studying
and incorporating ideas from other calculi which models dependent
types, and path-dependent types in particular.

>>>>

\section{Conclusion and Future Work}\label{conclusion}
This semester's work was instructive in pointing out the problematic
aspects of the original DOT calculus, and exploring some possible
fixes. However, I haven't been able to reach a revised calculus
without soundness hole. Furthermore, I believe that the revised
calculus with all the patches is not as elegant as the original
calculus. Going forward, I want to take a broader view by by studying
and incorporating ideas from other calculi which model dependent
types, and path-dependent types in particular.
